Deep Embedded Clustering for Open Cluster Characterization with Gaia DR2 Data

### 2021-04-07 paper/paper.tex

\documentclass[11pt,a4paper,english,twocolumn]{article}
\usepackage{unir_paper}
\usepackage{subcaption}
\usepackage{tablefootnote, multirow}

%---------------------------
%título del trabajo y autor
%---------------------------
\title{Deep Embedded Clustering for Open Cluster Characterization with Gaia DR2 Data}
\author{CD. Álvaro, C. Guzman, J. Álvaro}
\date{24th of January, 2021}

\resumen{
Characterize and understand \emph{Open Clusters} (OCs) allow us to understand better properties and mechanisms about the Universe such as stellar formation and the regions where these events occur. They also provide information about stellar processes and the evolution of the galactic disk.

In this paper, we present a novel method to characterize OCs. Our method employs a model built on \emph{Artificial Neural Networks} (ANNs). More specifically, we adapted a state of the art model, the \emph{Deep Embedded Clustering} (DEC) model for our purpose. The developed method aims to improve classical state of the arts techniques. We improved not only in terms of computational efficiency (with lower computational requirements), but in usability (reducing the number of hyperparameters to get a good characterization of the analyzed clusters). For our experiments, we used the \emph{Gaia DR2 database} as the data source, and compared our model with the clustering technique \emph{K-Means}. Our method achieves good results, becoming even better (in some of the cases) than current techniques.
}

\palabrasclave{
    characterization,
    data analysis,
    deep embedded clustering,
    gaia,
    machine learning,
    open cluster
}

\begin{document}
\twocolumn[
\begin{@twocolumnfalse}
\maketitle
\end{@twocolumnfalse}
]

@@

This paper is organized as follows. Section~\ref{sec:related_works} presents some related works and Section~\ref{sec:aims_and_method} describes in detail our model. The following Section~\ref{sec:results}, shows the results and compares them with a method that involves tools from the Virtual Observatory (VO) such as Clusterix~\cite{balaguer2020clusterix}. Finally, the last section concludes and outlines future research lines.

@@

%% Comparación con K-Means, DEC y DEC filter
\begin{figure*}[!htp]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/kmeans_pm_melotte_25.png}
      \includegraphics[width=\textwidth]{../figures/melotte_25/kmeans_hr_diagram_melotte_25.png}
      \caption{K-Means}
  \end{subfigure}
  \medskip
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_pm_melotte_25.png}
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_hr_diagram_melotte_25.png}
      \caption{DECOCC}
  \end{subfigure}
  \medskip
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_pm_filtered_melotte_25.png}
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_hr_diagram_filtered_melotte_25.png}
      \caption{DECOCC (filt.)}
  \end{subfigure}
  \caption{Evolution of Melotte 25 characterization}
  \label{fig:melotte_25_characterization_evolution}
\end{figure*}

@@

\newpage

@@

Our DECOCC model was implemented in Python 3.8 using the Keras 2.2 framework and Jupyter Notebooks~\cite{Kluyver2016jupyter}. All tests were run on an Apple Mac Pro Late 2013 with a 2.7GHz 12-Core Intel Xeon E5-2697v2, and 64GB RAM 1866MHz DDR3. For the GPU, we use a graphic card AMD FirePro D700 with 6GB~\footnote{All resources developed for this project are available at \href{https://github.com/cdalvaro/machine-learning-master-thesis}{https://github.com/cdalvaro/machine-learning-master-thesis}}.

@@

\begin{figure}[!hbt]
  % \centering
  % \begin{subfigure}[t]{0.30\textwidth}
  %   \centering
  %   \includegraphics[width=\textwidth]{../figures/melotte_25/dec_pm_melotte_25.png}
  % \end{subfigure}
  % \hfill
  % \begin{subfigure}[t]{0.30\textwidth}
    \centering
    \includegraphics[width=0.36\textwidth]{../figures/melotte_25/dec_parallax_melotte_25.png}
  % \end{subfigure}
  % \hfill
  % \begin{subfigure}[t]{0.30\textwidth}
  %   \centering
  %   \includegraphics[width=\textwidth]{../figures/melotte_25/dec_hr_diagram_melotte_25.png}
  % \end{subfigure}
  % \caption{Melotte 25 characterization.
  %          From left to right: proper motion configuration space,
  %          parallax histogram and H-R diagram.}
  \caption{Parallax histogram of Melotte 25 characterization.}
  \label{fig:result_melotte_25_dec}
\end{figure}

@@

%% comparativa de las figuras de los open clusters
\begin{figure*}[!hbt]
  \rotatebox[origin=c]{90}{{\bfseries NGC 2516}\strut}
  \rotatebox[origin=c]{90}{parallax \strut}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_parallax_ngc_2516.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_parallax_ngc_2516.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_parallax_filtered_ngc_2516.png}
  \end{subfigure}

  \rotatebox[origin=c]{90}{{\bfseries} \strut}
  \rotatebox[origin=c]{90}{hr diagram\strut}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_hr_diagram_ngc_2516.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_hr_diagram_ngc_2516.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_hr_diagram_filtered_ngc_2516.png}
  \end{subfigure}

  \rotatebox[origin=c]{90}{{\bfseries NGC 2632}\strut}
  \rotatebox[origin=c]{90}{parallax \strut}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_parallax_ngc_2632.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_ngc_2632.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_filtered_ngc_2632.png}
  \end{subfigure}

  \rotatebox[origin=c]{90}{{\bfseries} \strut}
  \rotatebox[origin=c]{90}{hr diagram\strut}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_hr_diagram_ngc_2632.png}
    \caption{K-Means}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_ngc_2632.png}
    \caption{DECOCC}
  \end{subfigure}%
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_filtered_ngc_2632.png}
    \caption{DECOCC (filt.)}
  \end{subfigure}
  \caption{Summary of the characterization for the clusters NGC 2516 and NGC 2632.}
  \label{fig:ngc_2516_ngc_2632_characterization_evolution}
\end{figure*}

\begin{figure*}[!hbt]
  \rotatebox[origin=c]{90}{{\bfseries NGC 2682}\strut}
  \rotatebox[origin=c]{90}{parallax \strut}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_parallax_ngc_2682.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_parallax_ngc_2682.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_parallax_filtered_ngc_2682.png}
  \end{subfigure}

  \rotatebox[origin=c]{90}{{\bfseries} \strut}
  \rotatebox[origin=c]{90}{hr diagram\strut}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_hr_diagram_ngc_2682.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_hr_diagram_ngc_2682.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_hr_diagram_filtered_ngc_2682.png}
  \end{subfigure}

  \rotatebox[origin=c]{90}{{\bfseries Melotte 22}\strut}
  \rotatebox[origin=c]{90}{parallax \strut}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/melotte_22/kmeans_parallax_melotte_22.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/melotte_22/dec_parallax_melotte_22.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/melotte_22/dec_parallax_filtered_melotte_22.png}
  \end{subfigure}

  \rotatebox[origin=c]{90}{{\bfseries} \strut}
  \rotatebox[origin=c]{90}{hr diagram\strut}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/melotte_22/kmeans_hr_diagram_melotte_22.png}
    \caption{K-Means}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/melotte_22/dec_hr_diagram_melotte_22.png}
    \caption{DECOCC}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \includegraphics[width=\textwidth]{../figures/melotte_22/dec_hr_diagram_filtered_melotte_22.png}
    \caption{DECOCC (filt.)}
  \end{subfigure}
  \caption{Summary of the characterization for the clusters NGC 2682 and Melotte 22.}
  \label{fig:melotte_22_ngc_2682_characterization_evolution}
\end{figure*}

@@

\renewcommand{\refname}{References}
\bibliographystyle{unsrt}
\bibliography{references}

>>>>

\documentclass[preprint,12pt,authoryear]{elsarticle}

\usepackage{subcaption}
\usepackage{tablefootnote, multirow}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}

\journal{Astronomy and Computing}

\begin{document}
\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%% \fntext[label3]{}

\title{Deep Embedded Clustering for Open Cluster Characterization with Gaia DR2 Data}

%\author[MET]{CD. Álvaro}

%\affiliation[MET]{organization={Meteologica},
             %addressline={Calle Costa Brava, 10},
             %city={Madrid},
             %postcode={28034},
             %country={Spain}}

%\author[UNAD,IAC]{C. Guzman}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%\affiliation[IAC]{organization={Instituto de Astrofisíca de Canarias},
%             addressline={Calle Vía Láctea, s/n},
%             city={ San Cristóbal de La Laguna},
%             postcode={ 38205},
%             country={Spain}}
%\affiliation[UNAD]{organization={Universidad Nacional Abierta y a Distancia},
%             addressline={Sede JCM Calle 14 Sur \# 14-23},
%             city={Bogotá},
%             country={Colombia}}

%\author[NIE,SEA,FAAE]{J. Álvaro}

%\affiliation[SEA]{organization={SEA Astronomia},
%             country={Spain}}

%\affiliation[NIE]{organization={Nodo Ibérico de Europlanet, Spain \& Portugal},
%             country={Spain / Portugal}}

%\affiliation[FAAE]{organization={Federación de Asociaciones Astronómicas de España},
%             addressline={C/ Serrano, n. 117},
%             city={Madrid},
%             postcode={28006},
%             country={Spain}}

% https://ascl.net/code/v/2823

% \date{24th of January, 2021}

\begin{abstract}
Characterize and understand \emph{Open Clusters} (OCs) allow us to understand better properties and mechanisms about the Universe such as stellar formation and the regions where these events occur. They also provide information about stellar processes and the evolution of the galactic disk.

In this paper, we present a novel method to characterize OCs. Our method employs a model built on \emph{Artificial Neural Networks} (ANNs). More specifically, we adapted a state of the art model, the \emph{Deep Embedded Clustering} (DEC) model for our purpose. The developed method aims to improve classical state of the arts techniques. We improved not only in terms of computational efficiency (with lower computational requirements), but in usability (reducing the number of hyperparameters to get a good characterization of the analyzed clusters). For our experiments, we used the \emph{Gaia DR2 database} as the data source, and compared our model with the clustering technique \emph{K-Means}. Our method achieves good results, becoming even better (in some of the cases) than current techniques.
\end{abstract}

%%Graphical abstract
% \begin{graphicalabstract}
% \includegraphics{grabs}
% \end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item We present a novel method to characterize Open Clusters
\item The method employs Artificial Neural Networks.
\item We adapted the Deep Embedded Clustering model.
\item Compare the results with K-Means using the Gaia DR2 database.
\item The code is freely available.
\end{highlights}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
 characterization \sep
    data analysis  \sep
    deep embedded clustering  \sep
    gaia  \sep
    machine learning  \sep
    open cluster
%% PACS codes here, in the form: \PACS code \sep code
% \PACS 0000 \sep 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
% \MSC 0000 \sep 1111
\end{keyword}

\end{frontmatter}

@@

This paper is organized as follows. Section~\ref{sec:related_works} presents some related works and Section~\ref{sec:aims_and_method} describes in detail our model. The following Section~\ref{sec:results}, shows the results using either the Melotte 25 dataset and a variety of clusters of different typologies. We also compare our model against a K-Means classification algorithm. Finally, the last section concludes and outlines future research lines.

@@

%% Comparación con K-Means, DEC y DEC filter
\begin{figure*}[!htbp]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/kmeans_pm_melotte_25.png}
      \includegraphics[width=\textwidth]{../figures/melotte_25/kmeans_hr_diagram_melotte_25.png}
      \caption{K-Means}
  \end{subfigure}
  \medskip
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_pm_melotte_25.png}
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_hr_diagram_melotte_25.png}
      \caption{DECOCC}
  \end{subfigure}
  \medskip
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_pm_filtered_melotte_25.png}
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_hr_diagram_filtered_melotte_25.png}
      \caption{DECOCC (filt.)}
  \end{subfigure}
  \caption{Evolution of Melotte 25 characterization}
  \label{fig:melotte_25_characterization_evolution}
\end{figure*}

@@

@@

Our DECOCC model was implemented in Python 3.8 using the Keras 2.2 framework and Jupyter Notebooks~\cite{Kluyver2016jupyter}. All tests were run on an Apple Mac Pro Late 2013 with a 2.7GHz 12-Core Intel Xeon E5-2697v2, and 64GB RAM 1866MHz DDR3. For the GPU, we use a graphic card AMD FirePro D700 with 6GB~\footnote{All resources developed for this project are available at [LINK]}.
%\href{https://github.com/cdalvaro/machine-learning-master-thesis}{https://github.com/cdalvaro/machine-learning-master-thesis}}.

@@

\begin{figure}[!hbt]
  % \centering
  % \begin{subfigure}[t]{0.30\textwidth}
  %   \centering
  %   \includegraphics[width=\textwidth]{../figures/melotte_25/dec_pm_melotte_25.png}
  % \end{subfigure}
  % \hfill
  % \begin{subfigure}[t]{0.30\textwidth}
    \centering
    \includegraphics[width=0.36\textwidth]{../figures/melotte_25/dec_parallax_melotte_25.png}
  % \end{subfigure}
  % \hfill
  % \begin{subfigure}[t]{0.30\textwidth}
  %   \centering
  %   \includegraphics[width=\textwidth]{../figures/melotte_25/dec_hr_diagram_melotte_25.png}
  % \end{subfigure}
  % \caption{Melotte 25 characterization. From left to right: proper motion configuration space, parallax histogram and H-R diagram.}
  \caption{Parallax histogram of Melotte 25 characterization.}
  \label{fig:result_melotte_25_dec}
\end{figure}

@@

%% comparativa de las figuras de los open clusters
\begin{figure*}[!hbt]
  \rotatebox[origin=c]{90}{{\bfseries NGC 2516}\strut}
  \rotatebox[origin=c]{90}{parallax \strut}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_parallax_ngc_2516.png}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_parallax_ngc_2516.png}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_parallax_filtered_ngc_2516.png}
  \end{subfigure}

  \rotatebox[origin=c]{90}{{\bfseries } \strut}
  \rotatebox[origin=c]{90}{hr diagram\strut}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_hr_diagram_ngc_2516.png}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_hr_diagram_ngc_2516.png}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_hr_diagram_filtered_ngc_2516.png}
  \end{subfigure}

  \rotatebox[origin=c]{90}{{\bfseries NGC 2632}\strut}
  \rotatebox[origin=c]{90}{parallax \strut}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_parallax_ngc_2632.png}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_ngc_2632.png}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_filtered_ngc_2632.png}
  \end{subfigure}

  \rotatebox[origin=c]{90}{{\bfseries } \strut}
  \rotatebox[origin=c]{90}{hr diagram\strut}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_hr_diagram_ngc_2632.png}
    \caption{K-Means}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_ngc_2632.png}
    \caption{DECOCC}
  \end{subfigure}%
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_filtered_ngc_2632.png}
    \caption{DECOCC (filt.)}
  \end{subfigure}
  \caption{Summary of the characterization for the clusters NGC 2516 and NGC 2632.}
  \label{fig:ngc_2516_ngc_2632_characterization_evolution}
\end{figure*}

\begin{figure*}[!hbt]
  \rotatebox[origin=c]{90}{{\bfseries NGC 2682}\strut}
  \rotatebox[origin=c]{90}{parallax \strut}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_parallax_ngc_2682.png}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_parallax_ngc_2682.png}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_parallax_filtered_ngc_2682.png}
  \end{subfigure}

  \rotatebox[origin=c]{90}{{\bfseries } \strut}
  \rotatebox[origin=c]{90}{hr diagram\strut}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_hr_diagram_ngc_2682.png}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_hr_diagram_ngc_2682.png}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_hr_diagram_filtered_ngc_2682.png}
  \end{subfigure}

  \rotatebox[origin=c]{90}{{\bfseries Melotte 22}\strut}
  \rotatebox[origin=c]{90}{parallax \strut}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/melotte_22/kmeans_parallax_melotte_22.png}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/melotte_22/dec_parallax_melotte_22.png}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/melotte_22/dec_parallax_filtered_melotte_22.png}
  \end{subfigure}

  \rotatebox[origin=c]{90}{{\bfseries } \strut}
  \rotatebox[origin=c]{90}{hr diagram\strut}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/melotte_22/kmeans_hr_diagram_melotte_22.png}
    \caption{K-Means}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/melotte_22/dec_hr_diagram_melotte_22.png}
    \caption{DECOCC}
  \end{subfigure}
  \begin{subfigure}{0.29\textwidth}
    \includegraphics[width=\textwidth]{../figures/melotte_22/dec_hr_diagram_filtered_melotte_22.png}
    \caption{DECOCC (filt.)}
  \end{subfigure}
  \caption{Summary of the characterization for the clusters NGC 2682 and Melotte 22.}
  \label{fig:melotte_22_ngc_2682_characterization_evolution}
\end{figure*}

@@

\section{Acknowledgements}

This work has made use of data from the European Space Agency (ESA) mission
 Gaia (\url{https://www.cosmos.esa.int/gaia}), processed by the Gaia
Data Processing and Analysis Consortium (DPAC\footnote{ \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}}). Funding for the DPAC
has been provided by national institutions participating in the {\it Gaia} Multilateral Agreement.

% \renewcommand{\refname}{References}
\bibliographystyle{elsarticle-harv}
\bibliography{references}
